---
title: "Running lintr with box.linters on a project"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Running lintr with box.linters on a project}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Setup box.linters

The function [`use_box_lintr()`](https://appsilon.github.io/box.linters/reference/use_box_lintr.html) creates a minimal `.lintr` config file.

```{r usage, eval = FALSE}
box.linters::use_box_lintr()
```

This would create a `.lintr` file in your project root:

```{yaml}
linters:
  linters_with_defaults(
    defaults = box.linters::box_default_linters
  )
encoding: "UTF-8"
```

## Active `box`-compatible linters

Because [`lintr::object_usage_linter()`](https://lintr.r-lib.org/reference/object_usage_linter.html) is not compatible with `box`, the following linter functions are provided in place of `object_usage_linter()`. Examples of what are considered lint are included in the function reference pages.

* [`box_pkg_fun_exists_linter()`](https://appsilon.github.io/box.linters/reference/box_pkg_fun_exists_linter.html)
* [`box_unused_att_mod_obj_linter()`](https://appsilon.github.io/box.linters/reference/box_unused_att_mod_obj_linter.html)
* [`box_unused_att_pkg_fun_linter()`](https://appsilon.github.io/box.linters/reference/box_unused_att_pkg_fun_linter.html)
* [`box_unused_attached_mod_linter()`](https://appsilon.github.io/box.linters/reference/box_unused_attached_mod_linter.html)
* [`box_unused_attached_pkg_linter()`](https://appsilon.github.io/box.linters/reference/box_unused_attached_pkg_linter.html)
* [`box_usage_linter()`](https://appsilon.github.io/box.linters/reference/box_usage_linter.html)
* [`r6_usage_linter()`](https://appsilon.github.io/box.linters/reference/r6_usage_linter.html)
* [`unused_declared_object_linter()`](https://appsilon.github.io/box.linters/reference/unused_declared_object_linter.html)

## Run lintr

Use `lintr` functions to lint a file or a directory.

```{r runlint, eval = FALSE}
# Lint a file
lintr::lint("some_file.R")

# Lint a directory
lintr::lint_dir("some_dir")
```
