---
title: "Running lintr with box.linters on a rhino project"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Running lintr with box.linters on a rhino project}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Rhino (>= 1.8.0)

> Rhino 1.8.0 may not yet be available at the time of this release.

Projects created with `rhino` version 1.8.0 and later come preconfigured with a `.lintr` file. 

```{yaml}
linters:
  linters_with_defaults(
    defaults = box.linters::rhino_default_linters,
    line_length_linter = lintr::line_length_linter(100)
  )
```

## Using `box.linters` with an existing Rhino (< 1.8.0) project

Refer to the [Rhino 1.8 Migration Guide](https://appsilon.github.io/rhino/articles/how-to/migrate-1-8.html) to upgrade to the latest version.

The following code is used to setup your `.lintr` config file.

```{r, eval = FALSE}
box.linters::use_box_lintr(type = "rhino")
```

## Active `box`-compatible linters for `rhino`

All linter functions included in the `box.linters` package are activated for Rhino projects. Please refer to the [Rhino style guide](https://appsilon.github.io/rhino/articles/explanation/rhino-style-guide.html) for more information.

## Linting a Rhino project

Use the helper function included in the `rhino` package to lint your Rhino project.

```{r, eval = FALSE}
rhino::lint_r()
```
